How to compute the fusion product of MV cycles in type A

### 2021-03-29 draft.tex
major overhaul in the sage folder
unappedicized appendix

\jcom{I changed this a bit in order to match Mirkovic-Vilonen better.}
% =======
% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% >>>>>>> 5a15ce15b14109bab482282aa5657c9596f7892d

@@

% TODO: un-appendicize 
\appendix

\section{Generalized orbital varieties?}
TODO: recall $\tau\mapsto X_\tau \mapsto Z_\tau$

@@

\section{Tableaux and families}

@@

    Need that the operations of taking quotients and taking generalized eigenspaces (i.e.\ $-\otimes\CC\xt[t-a]$) commute.
\end{proof}

\begin{question}[Related question]
    If $\mu_1,\mu_2$ are not dominant, the LHS is smaller so the map $?$ has no chance of being an isomorphism. In general the map $?$ has to do with producing a matrix from a linear operator. 
    \[
    \begin{tikzcd}
        \overline\Gr^{\lambda_1,\lambda_2}_{0,s}\cap S^{\mu_1,\mu_2}_{0,s} \ar[r,equals]\ar[d] & \overline\Gr^{\lambda_1} \cap S^{\mu_1} \times \overline\Gr^{\lambda_2} \cap S^{\mu_2} \supset Z_1 \times Z_2 \ar[d]\\
        \overline\OO^{\lambda_1,\lambda_2} \cap \UU^{\mu_1,\mu_2} \ar[r,"?"] & \overline\OO^{\lambda_1}\cap \TT_{\mu_1}\cap \n \times \overline\OO^{\lambda_2}\cap \TT_{\mu_2}\cap \n
    \end{tikzcd}    
    \]
\end{question}

\section{Examples}
\rcom{I have 3 examples in mind right now: fusion product producing 1 term (maybe $1 \leftarrow 2 * 1 \rightarrow 2$), fusion product producing more than 1 term $(S_1 * S_2)$, and fusion product with multiplicities $((S_1 * S_2)^2)$}

>>>>

\jcom{I changed this a bit in order to match Mirkovic--Vilonen better.}
% =======
% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% >>>>>>> 5a15ce15b14109bab482282aa5657c9596f7892d

@@

% TODO: un-appendicize 
% \appendix

\subsection{Generalized orbital varieties?}
TODO: recall $\tau\mapsto X_\tau \mapsto Z_\tau$

@@

\subsection{Tableaux and families}

@@

    Need: operations of taking quotients and taking generalized eigenspaces (i.e.\ $-\otimes\CC\xt[t-a]$) commute.

    \acom{Does this have to do with the fact that a functor $F: \sch \to \set$ commutes with projective limit if and only if it's representable?}
\end{proof}

\begin{question}[Related question]
    If $\mu_1,\mu_2$ are not dominant, the LHS is smaller so the map $?$ has no chance of being an isomorphism. In general the map $?$ has to do with producing a matrix from a linear operator. 
    \[
    \begin{tikzcd}
        \overline\Gr^{\lambda_1,\lambda_2}_{0,s}\cap S^{\mu_1,\mu_2}_{0,s} \ar[r,equals]\ar[d] & \overline\Gr^{\lambda_1} \cap S^{\mu_1} \times \overline\Gr^{\lambda_2} \cap S^{\mu_2} \supset Z_1 \times Z_2 \ar[d]\\
        \overline\OO^{\lambda_1,\lambda_2}_{0,s} \cap \UU^{\mu_1,\mu_2}_{0,s} \ar[r,"?"] & \overline\OO^{\lambda_1}\cap \TT_{\mu_1}\cap \n \times \overline\OO^{\lambda_2}\cap \TT_{\mu_2}\cap \n
    \end{tikzcd}    
    \]
\end{question}

\subsection{Examples}
\rcom{I have 3 examples in mind right now: fusion product producing 1 term (maybe $1 \leftarrow 2 * 1 \rightarrow 2$), fusion product producing more than 1 term $(S_1 * S_2)$, and fusion product with multiplicities $((S_1 * S_2)^2)$}
